---
output: github_document
bibliography: references.bib
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(kableExtra)
```

# shadowVIMP - Simulation Study

<!-- badges: start -->
<!-- badges: end -->

This repository contains the code for the simulation study conducted in [PAPER TITLE]. The most important files in this repository are:

1. File `01_sim.R` specifies the data simulation scenarios along with the methods for performing feature selection.
2. File `02_unpack_resuts.R` gathers the results obtained in the first file and computes performance measures for all scenarios.
3. File `03_alzheimer` performs feature selection using the shadowVIMP method on the Alzheimer dataset from the `AppliedPredictiveModeling` package.

The below table contains the details of the data simulation designs and feature selection methods that are specified in the `01_sim.R` file.

```{r table_simulations_methods, echo=FALSE}
methods_set1 <- c("shadowVIMP without pre-selection", 
             "shadowVIMP with pre-selection", 
             "Boruta algorithm with 10.000 trees [@kursa2010boruta, @kursa2010feature]", 
             "Boruta algorithm with 500 trees [@kursa2010boruta, @kursa2010feature]", 
             "Method from @janitza2018computationally with 10.000 trees")

methods_set2 <- c("shadowVIMP without pre-selection", 
             "shadowVIMP with pre-selection", 
             "Boruta algorithm with 10.000 trees [@kursa2010boruta, @kursa2010feature]", 
             "Boruta algorithm with 500 trees [@kursa2010boruta, @kursa2010feature]",
             "Method from @hapfelmeier2023efficient with 10.000 trees, implemented in @hapfelmeier2023package",
             "Method from @hapfelmeier2023efficient with 500 trees, implemented in @hapfelmeier2023package"
             )

table_content <- data.frame(
  data_sim = c(rep("@degenhardt2019evaluation with a group size of 50, 100 observations, and a total of 5.000 covariates.", 5),
               rep("@friedman1991multivariate with 100 observations", 6),
               rep("@degenhardt2019evaluation with a group size of 10, 100 observations, and a total of 5.000 covariates.", 5),
               rep("@strobl2007bias with 100 observations", 6),
               rep("The null case of the design @nicodemus2010behaviour", 6)
               ),
  method = c(methods_set1, methods_set2, methods_set1, methods_set2, methods_set2),
  name = paste0("evaluatesetting", 1:28)
)


names(table_content) <- c("Data Simulation Design", "Method", "Setting Name in `01_sim.R`")

kable(table_content, "html", escape = FALSE, align = "c") %>%
  collapse_rows(columns = 1, valign = "middle") %>% 
  column_spec(1, width = "20em") %>%  # Adjust width of the first column
  kable_styling(full_width = FALSE)

```

The remainder of the repository has the following structure:

* Folder `code_rfvarse` stores the numeric results of all analyzed data simulation designs and feature selection algorithms, grouped into subfolders according to the data simulation design.
* Folder `functions` contains the code for all custom functions used in this study.
* The "xls" files store performance measures for both the proposed method and established methods, as created in the `01_sim.R` file.


